Considering scale in multilayer animal social networks

### 2020-06-22 paper/manuscript.Rmd
more social p

<!-- intro -->
Complex animal social systems are influenced by biological and observation scales.
By parsing social systems into contexts using multilayer networks,
we observed differences across social, spatial and temporal scales.
Social scale
Spatial and temporal contexts 
including habitats, discrete patches and fragmented landscapes, as well as across 
seasonal differences in resource availability, or periods of migration, aggregation and disaggregation [@Kivela_2014; @Porter_2018; @Pilosof_2017]. 
Sociality exists across scales characterized by different 
types of behaviours as well as spatial and temporal thresholds defining these. 
Our results highlight the influence of social, spatial and temporal scales
on multilayer animal social networks, showing a requirement to consider biologically
relevant scales when selecting observational scales for a given study. 
<!-- intro -->

<!-- social scale -->
Defining the social scale to generate networks is an
essential consideration for social network analysis <!-- with direct impacts on
outcomes blah-->[@Castles_2014; @Carter_2015; @Farine_2015a]. Proximity-based
social networks generated using GPS location data require using a social scale,
specifically a social distance threshold, to define social associations. We
found increasing individual graph strength across three habitat layers with
increasing social distance threshold (Figure \@ref(fig:socres)). <!-- This means blah blah for different types of interactions.--> In addition, 
habitat layers differed in their response to social distance threshold, with
open and foraging with a larger increase in graph strength and greater variation
across individuals. <!-- What could this mean biologically? --> These results emphasize that multilayer network metrics are
directly influenced by social scale, in this case the spatial distance
threshold.
<!-- social scale -->

<!-- drop 
Our results highlight the influence of social, spatial and temporal scale on
multilayer networks. For social scale, we found individuals became more
connected with increasing social distance threshold. Increasing land cover
resolution lead to a decrease in availability of patchy and rare habitats and,

QW: not sure I'd mention 'rare' since there are only 3 habitat types. 
Could you just say 'less common' or even just 'patchy'?

correspondingly, lower connectivity of individuals in these habitats. Temporal
windows highlighted clear periods of increased sociality among individuals.
Finally, increasing number of observations led to a general stabilization in network
metrics. As such, scale is inherently tied to the generation  of multilayer
networks and metrics evaluating them, as well as the individual layers that make
them up.
-->

Social structure and habitat selection are intimately related: individuals must
share space to interact and the distribution of resources influences group
dynamics and home range size [@Webber_2018]. Social structure is influenced by
resource availability and seasonality [@Peignier_2019], configuration [@He_2019]
and fragmentation [@Banks_2007]. Habitat selection, the disproportionate use of
available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
is a scale-dependent process [@Mayor_2009]. Johnson (1980) identified four orders of habitat selection: (1)
the geographical range of a species, (2) the home range of an individual, the
(3) habitat patches within the home range and (4) specific resources within a
habitat patch. Kie et al. [-@Kie_2002] found that, independently, third order of
selection was insufficient for capturing landscape attributes selected for by
mule deer (*Odocoileus hemionus*), at a scale larger than their home range size.
Moving past this hierarchical perspective, Mayor (2007) emphasized the
importance of considering a broad continuum of scales to reveal scale-dependent
selection and avoid the bias of predefined scales assumed to be associated with
certain behaviours.

>>>>

<!-- intro -->
<!-- QW: could focus on just talking about the importance of scale for behavioural and spatial ecology. Why is it important and what are the more broadly applicable ideas that lead us to this paper -->

Complex animal social systems are influenced by biological and observation scales.
By parsing social systems into contexts using multilayer networks,
we observed differences across social, spatial and temporal scales.
Social scale
Spatial and temporal contexts 
including habitats, discrete patches and fragmented landscapes, as well as across 
seasonal differences in resource availability, or periods of migration, aggregation and disaggregation [@Kivela_2014; @Porter_2018; @Pilosof_2017]. 
Sociality exists across scales characterized by different 
types of behaviours as well as spatial and temporal thresholds defining these. 
Our results highlight the influence of social, spatial and temporal scales
on multilayer animal social networks, showing a requirement to consider biologically
relevant scales when selecting observational scales for a given study. 
<!-- intro -->

<!-- social scale -->
Social scale is essential consideration for
social network analysis [@Castles_2014; @Carter_2015; @Farine_2015a].
Proximity-based social networks generated using GPS location data use a social
distance threshold to define social associations. Increasing the social distance threshold
resulted in an increase in graph strength 
across all three habitat layers  (Figure
\@ref(fig:socres)). <!-- This means blah blah for different types of
interactions.--> However, habitat layers differed in their response to
increasing social distance threshold, with open and foraging with a larger
increase in graph strength and greater variation across individuals. 
<!-- What could this mean biologically? --> These results emphasize that multilayer
network metrics are directly influenced by social scale. In extension, 
caribou relocations could be classified into behavioural states using hidden
Markov models to explore the influence of behavioural states on social scale 
in a multilayer network [see @Jones_2020]. 
<!-- social scale -->

<!-- habitat+social -->
Social structure and habitat selection are intimately related: individuals must
share space to interact and the distribution of resources influences group
dynamics and home range size [@Webber_2018]. Social structure is influenced by
resource availability and seasonality [@Peignier_2019], configuration [@He_2019]
and fragmentation [@Banks_2007]. Habitat selection, the disproportionate use of
available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
is a scale-dependent process [@Mayor_2009]. 
Johnson (1980) identified four orders of habitat selection: (1)
the geographical range of a species, (2) the home range of an individual, the
(3) habitat patches within the home range and (4) specific resources within a
habitat patch. <!--Kie et al. [-@Kie_2002] found that, independently, third order of
selection was insufficient for capturing landscape attributes selected for by
mule deer (*Odocoileus hemionus*), at a scale larger than their home range size.-->
Moving past this hierarchical perspective, Mayor (2007) emphasized the
importance of considering a broad continuum of scales to reveal scale-dependent
selection and avoid the bias of predefined scales assumed to be associated with
certain behaviours.
